%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Artificial Intelligence Intern} % Job title
    {Bank of the Philippine Islands (BPI)} % Organization
    {Makati city, Philippines} % Location
    {Apr. 2023 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated within two key teams, focusing on code completion/automation and retirement solutions, actively contributing to ideation process and presenting data-driven solutions to C-level executive.}
        \item { Utilized geopandas library to analyze geospatial data and identify potential profitable business partners by visually plotting mall locations.}
        \item {Leveraged web scraping techniques with BeautifulSoup4 to extract 1000+ listings from websites, ensuring accurate and reliable extraction, and subsequently cleaned the collected data.}
        \item {Performed data wrangling tasks using Python libraries and Jupyter Notebooks to clean, preprocess, and transform diverse datasets efficiently.}
        \item {Actively participated in machine learning workshops focused on the foundations of AI and machine learning, gaining a comprehensive understanding of key concepts, and practical applications.}
        \item {Conducted interviews with cross-functional teams to identify areas or tasks within the company that could be improved through AI or automation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Website Manager} % Job title
    {XXD Global Trading} % Organization
    {Las Piñas, Philippines} % Location
    {Jun. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop and manage an e-commerce platform to increase online sales.}
        \item {Implement and execute SEO strategies to improve search engine rankings and drive traffic to the website.}
        \item {Monitor website analytics and performance metrics to ensure maximum visibility and engagement.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Office Assistant} % Job title
    {Philippine Red Cross QC} % Organization
    {Quezon city, Philippines} % Location
    {Nov. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Effectively communicated with external partners, fostering strong partnerships and coordinating their events with the Philippine Red Cross.}
        \item {Collaborated seamlessly with cross-functional teams, ensuring smooth execution of tasks and efficient organization of paperwork.}
      \end{cvitems}
    }
%---------------------------------------------------------

    


\end{cventries}
